---
title: "Darwin"
author: "GG"
date: "5/8/2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Darwin Correlation Analyses
```{r}
library(ggplot2)
library(tidyverse)
library(readxl)
library(janitor)
library(dbplyr)
```
Throughout this code I reference my computer desktop for reading and saving files, however the data files are available in github and can be accessed with a quick modification to the code.
```{r}
darwin <- read_csv("~/Documents/darwin_stats2.csv")
```
Creating a correlation matrix

```{r}
corr <- round(cor(darwin), 1)
```

```{r}
install.packages("ggcorrplot")
library(ggcorrplot)
corr <- round(cor(darwin), 1)
```
```{r}
p.mat <- cor_pmat(darwin)
p.mat

```

This figure includes the r values. These values can be removed by elimiating the lab = TRUE assignment
```{r}
darwin_corr <- ggcorrplot(corr, hc.order = TRUE, 
           type = "lower", 
           lab = TRUE, 
           lab_size = 3, outline.col = "white",
           p.mat = p.mat,
           title="Correlogram of Lionfish Density", 
           colors = c("darkblue", "white", "red"),
           ggtheme=theme_bw)
darwin_corr
ggsave(darwin, plot = darwin_corr, device = "eps", path = "~/Desktop/Lionfish")
```



In order to create the biplot we need devtools and ggbiplot available from CRAN and github
```{r}
install.packages(https://github.com/r-lib/devtools.git)
```

Here we run a PCA analysis with eigenvalues and incorporate lionfish density

This is the code used to create the factanal pca plot used in the manuscript using darwin_stats2 datafile
```{r}
darwin.pca3 <- darwin[,2:8]
darwin.pca3[6] = NULL
darwin.pca3[5] = NULL
d.factanal <- factanal(darwin.pca3, factors = 2, scores = 'regression')
pca.plot <- autoplot(d.factanal, data = darwin, colour = 'lionfish_den', size = 3,
         loadings = TRUE, loadings.label = TRUE, loadings.label.size  = 5) + theme_classic()
pca.plot
```

```{r}
fit2 <- glm((lionfish_den + 1)~fish_bio, data=darwin, family = Gamma())
fit2
```

```{r}
hist(resid(fit2))
qqnorm(resid(fit2))
qqline(resid(fit2))
```

```{r}

AIC(fit2)
summary(fit2)
```

GLM model with all variables included showing covariance among possible drivers. 
```{r}
scale((darwin[,2:8]), center = TRUE, scale = TRUE)
fit3 <- glm((lionfish_den + 1)~fish_bio+fish_den+p_furc+fish_div+temp, data=darwin, family = Gamma())
summary(fit3)
```

```{r}
install.packages('data.table')
library(car)
sqrt(vif(fit3))
```

```{r}
darwin3 <- read_csv("~/Documents/darwin_stats2.csv")
scale((darwin3[,2:8]), center = TRUE, scale = TRUE)
fit_bio2 <- glm((lionfish_den + 1)~fish_bio, data=darwin3, family = Gamma())
fit_den2 <- glm((lionfish_den + 1)~fish_den, data=darwin3, family = Gamma())
fit_div2 <- glm((lionfish_den + 1)~fish_div, data=darwin3, family = Gamma(), start = c(0.5, 0.5))
fit_pfur2 <- glm((lionfish_den + 1)~p_furc, data=darwin3, family = Gamma())
fit_temp2 <- glm((lionfish_den + 1)~temp, data=darwin3, family = Gamma())
AIC(fit_bio2, fit_den2, fit_div2, fit_pfur2, fit_temp2)
coef(fit_bio2, fit_den2, fit_div2, fit_pfur2, fit_temp2)
```
```{r}
coef(fit_bio2) 
coef(fit_den2)
coef(fit_div2)
coef(fit_pfur2) 
coef(fit_temp2)
```


