---
title: "Darwin"
author: "GG"
date: "5/8/2018"
output:
  pdf_document: default
  html_document: default
---
#Darwin Correlation Analyses
```{r}
library(ggplot2)
library(tidyverse)
library(readxl)
library(janitor)
library(dbplyr)
```

```{r}
darwin <- read_csv("~/Documents/darwin_stats.csv")
```
Creating a correlation matrix

```{r}
corr <- round(cor(darwin), 1)
```

```{r}
install.packages("ggcorrplot")
library(ggcorrplot)
corr <- round(cor(darwin), 1)
```
```{r}
p.mat <- cor_pmat(darwin)
p.mat

```


```{r}
darwin_corr <- ggcorrplot(corr, hc.order = TRUE, 
           type = "lower", 
           outline.col = "white",
           p.mat = p.mat,
           title="Correlogram of Lionfish Density", 
           colors = c("darkblue", "white", "red"),
           ggtheme=theme_bw)
darwin_corr
ggsave(darwin, plot = darwin_corr, device = "eps", path = "~/Desktop/Lionfish")
```

Now running a permanova on variables main driving variable to determine relative influence on lionfish densities. Log transforming the data in order to normalize variance.  
```{r}
library(vegan)
perma <- adonis(dist(lionfish_den) ~ log(p_furc + 1)+log(fish_den +1) + log(fish_bio + 1) + log(fish_div + 1) + log(temp + 1), data=darwin, permutations=100000)
perma
#keep this one - this is the best and makes the most sense based on the correlation matrix
```

Visualizing the permanova resutls with a PCA analysis - using log tranformation to driver variables
```{r}
# log transform 
log.lion <- log(darwin[, 2:8] + 1)
log.lion[6] = NULL
log.lion[5] = NULL
darwin.den <- darwin[, 1]
 
# apply PCA - scale. = TRUE is highly 
# advisable, but default is FALSE. 
darwin.pca <- prcomp(log.lion,
                 center = TRUE,
                 scale. = TRUE) 
```


```{r}
# print method
print(darwin.pca)
```


```{r}
# plot method
plot(darwin.pca, type = "l")
```
In order to create the biplot we need devtools and ggbiplot available from CRAN and github
```{r}
install.packages(https://github.com/r-lib/devtools.git)
```

```{r}
library(devtools)
install_github("vqv/ggbiplot")
 
library(ggbiplot)
g <- ggbiplot(darwin.pca, obs.scale = 1, var.scale = 1, 
              groups = as.character(darwin.den), ellipse = FALSE, 
              circle = FALSE)
g <- g + scale_color_discrete(name = '')
g <- g + theme(legend.direction = 'horizontal', 
               legend.position = 'top')
print(g)

```
This is a standard PCA visualization with eigenvalues
```{r}
library(ggfortify)
autoplot(darwin.pca, loadings = TRUE, loadings.colour = 'blue', size = 3,
         loadings.label = TRUE, loadings.label.size = 5)
```
Here we include lionfish density
```{r}
d.factanal <- factanal(log.lion, factors = 2, scores = 'regression')
pca.plot <- autoplot(d.factanal, data = darwin, colour = 'lionfish_den', size = 3,
         loadings = TRUE, loadings.label = TRUE, loadings.label.size  = 5) + theme_classic()
pca.plot
ggsave(darwin, plot = pca.plot, device = "eps", path = "~/Desktop/Lionfish")
```

Throughout this code I reference my computer desktop for reading and saving files, however the data files are available in github and can be accessed with a quick modification to the code. 


```{r}
library(vegan)
perma3 <- adonis(dist(lionfish_den) ~ (fish_bio), data=darwin, permutations=999)
perma3
#untranformed data
```

```{r}
darwin.pca2 <- darwin[,2:8]
d.factanal <- factanal(darwin.pca2, factors = 2, scores = 'regression')
pca.plot <- autoplot(d.factanal, data = darwin, colour = 'lionfish_den', size = 3,
         loadings = TRUE, loadings.label = TRUE, loadings.label.size  = 5) + theme_classic()
pca.plot
```

```{r}
fit <- glm((lionfish_den + 1)~fish_bio, data=darwin, family = Gamma())
fit
```

```{r}
hist(resid(fit))
qqnorm(resid(fit))
qqline(resid(fit))
```

```{r}

AIC(fit)
summary(fit)
```
```{r}
scale((darwin[,2:8]), center = TRUE, scale = TRUE)
fit2 <- glm((lionfish_den + 1)~fish_bio+fish_den+p_furc+fish_div+temp, data=darwin, family = Gamma())
summary(fit2)
```

```{r}
install.packages('data.table')
library(car)
sqrt(vif(fit2))
```

```{r}
darwin2 <- read_csv("~/Documents/darwin_stats.csv")
fit_bio <- glm((lionfish_den + 1)~fish_bio, data=darwin2, family = Gamma())
fit_den <- glm((lionfish_den + 1)~fish_den, data=darwin2, family = Gamma())
fit_div <- glm((lionfish_den + 1)~fish_div, data=darwin2, family = Gamma())
fit_pfur <- glm((lionfish_den + 1)~p_furc, data=darwin2, family = Gamma())
fit_temp <- glm((lionfish_den + 1)~temp, data=darwin2, family = Gamma())
AIC(fit_bio, fit_den, fit_pfur, fit_temp)
coef(fit_bio, fit_den, fit_pfur, fit_temp)
```
```{r}
coef(fit_bio) 
coef(fit_den) 
coef(fit_pfur) 
coef(fit_temp)
```
```{r}
fit_bio <- glm((lionfish_den + 1)~fish_bio, data=darwin2)
fit_den <- glm((lionfish_den + 1)~fish_den, data=darwin2)
fit_div <- glm((lionfish_den + 1)~fish_div, data=darwin2)
fit_pfur <- glm((lionfish_den + 1)~p_furc, data=darwin2)
fit_temp <- glm((lionfish_den + 1)~temp, data=darwin2)
AIC(fit_bio, fit_den, fit_div, fit_pfur, fit_temp)
```

