---
title: "heatmap_final"
author: "GG"
date: "1/28/2019"
output: 
  pdf_document: default
  html_document: default
  word_document: default
---
Loading Libraries
```{r}
library(ggplot2)
library(tidyverse)
library(readxl)
library(janitor)
library(dbplyr)
```

Input datafile from computer
```{r}
heatmap <- read_csv("~/Desktop/Lionfish/Heatmap data.csv")
```

plot data
Basic Heatplot
```{r}
ggplot(data = heatmap, aes(x = site, y = species)) + geom_tile(aes(fill = mean))
```
Changing color schemes
```{r}
ggplot(data = heatmap, aes(x = site, y = species)) + geom_tile(aes(fill = mean), color = "white") +
  scale_fill_gradient(low = "white", high = "darkred") +
  ylab("Species") +
  xlab("") +  
  theme(legend.title = element_text(size = 10),
        legend.text = element_text(size = 12),
        plot.title = element_text(size=16),
        axis.title=element_text(size=14,face="bold"),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(fill = "Percent")
```
Changing the order of the fish species
```{r}
ggplot(data = heatmap, aes(x = site, y = species)) + geom_tile(aes(y = reorder(species, mean, median, order = TRUE), fill = mean), color = "white") +
  scale_fill_gradient(low = "white", high = "darkblue") +
  ylab ("Species") +
  xlab("") +  
  theme(legend.title = element_text(size = 10),
        legend.text = element_text(size = 12),
        plot.title = element_text(size=16),
        axis.title=element_text(size=14,face="bold"),
        axis.text.x = element_text(angle = 45, hjust = 1),
axis.text.y=element_text(face="italic")) +
  labs(fill = "Percent")
```

First version sent to review

```{r}
heatmap_plot_red <- ggplot(data = heatmap, aes(x = site, y = species)) + geom_tile(aes(y = reorder(species, mean, order = TRUE), fill = mean), color = "white") +
  scale_fill_gradient(low = "white", high = "red") +
  ylab ("Species") +
  xlab("") +  
  theme(legend.title = element_text(size = 10),
        legend.text = element_text(size = 12),
        plot.title = element_text(size=16),
        axis.title=element_text(size=14,face="bold"),
        axis.text.x = element_text(angle = 45, hjust = 1),
axis.text.y=element_text(face="italic")) +
  labs(fill = "Percent")
heatmap_plot_red
ggsave(plot = heatmap_plot_red, path= "~/Desktop/Lionfish", filename = "heatmap_plot_red_rev.eps", device = "eps")
```

Modifications made based on reviewer comments, including changing the x-axis to reorder sites in clockwise location around Bermuda and using mean instead of median for the order of the species. 

```{r}
# reorder x axis to go around the platform
# mtcars$cyl2 <- factor(mtcars$cyl, levels = c("6","4","8"))
heatmap$site <- as.character(heatmap$site)
heatmap$site <- factor(heatmap$site, levels = c("Angel", "Dark_Slime", "N_Rock", "Reel_Sticky", "NNE", "XL", "Coopers", "Tuckers", "Spittal", "Elbow", "Tiger"))
heatmap_plot_rev <- ggplot(data = heatmap, aes(x = site, y = species)) + geom_tile(aes(y = reorder(species, mean, order = TRUE), fill = mean), color = "white") +
  scale_fill_gradient(low = "white", high = "red") +
  ylab ("Species") +
  xlab("") + theme_classic() +
  theme(legend.title = element_text(size = 10),
        legend.text = element_text(size = 12),
        plot.title = element_text(size=16),
        axis.title=element_text(size=14,face="bold"),
        axis.text.x = element_text(angle = 45, hjust = 1),
axis.text.y=element_text(face="italic")) +
  labs(fill = "Percent")
heatmap_plot_rev
ggsave(plot = heatmap_plot_rev, path= "~/Desktop/Lionfish", filename = "heatmap_plot_rev.eps", device = "eps")
```

Adjusting colors and font size

```{r}
heatmap$site <- as.character(heatmap$site)
heatmap$site <- factor(heatmap$site, levels = c("Angel", "Dark_Slime", "N_Rock", "Reel_Sticky", "NNE", "XL", "Coopers", "Tuckers", "Spittal", "Elbow", "Tiger"))
heatmap_plot_revBP <- ggplot(data = heatmap, aes(x = site, y = species)) + geom_tile(aes(y = reorder(species, mean, order = TRUE), fill = mean), color = "white") +
  scale_fill_gradient2(low = "white", high = "darkred", mid = "red", midpoint = 0.31) +
  ylab ("Species") +
  xlab("") + theme_classic() +
  theme(legend.title = element_text(size = 10),
        legend.text = element_text(size = 12),
        plot.title = element_text(size=16),
        axis.title=element_text(size=14),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
axis.text.y=element_text(face="italic", size = 12)) +
  labs(fill = "Percent Contribution")
heatmap_plot_revBP
ggsave(plot = heatmap_plot_revBP, path= "~/Desktop/Lionfish", filename = "heatmap_final.eps", device = "eps")

```
Final Version in publication
```{r}
heatmap$site <- as.character(heatmap$site)
heatmap$site <- factor(heatmap$site, levels = c("Angel", "Dark_Slime", "N_Rock", "Reel_Sticky", "NNE", "XL", "Coopers", "Tuckers", "Spittal", "Elbow", "Tiger"))
heatmap_plot_revBP <- ggplot(data = heatmap, aes(x = site, y = species)) + geom_tile(aes(y = reorder(species, mean, order = TRUE), fill = mean), color = "white") +
  scale_fill_gradient2(low = "white", high = "darkred", mid = "red", midpoint = 0.31) +
  ylab ("Species") +
  xlab("") + theme_bw() +
  theme(legend.title = element_text(size = 10),
        legend.text = element_text(size = 12),
        plot.title = element_text(size=16),
        axis.title=element_text(size=14),
        axis.text.x = element_text(angle = 45, hjust = 1),
axis.text.y=element_text(face="italic")) +
  labs(fill = "Percent Contribution")
heatmap_plot_revBP
ggsave(plot = heatmap_plot_revBP, path= "~/Desktop/Lionfish", filename = "heatmap_final2.eps", device = "eps")

```